Model LF

### 2022-12-15 Paper version rmd.Rmd
Commit

COMMENT> 
BEHAVIORAL> lf_test
TSRANGE 2005 3 2020 1
EQ> lf_test = theta_00 + theta_01 * TSLAG(ur_ds,1)
COEFF> theta_00 theta_01
STORE> coe(102)

@@

COMMENT> 
IDENTITY> lf
EQ> lf = (part*pop)/1000
IF> shock_part_model <=0
IDENTITY> lf
EQ> lf = (part1*pop*(1-old_age_ratio))/1000
IF> shock_part_model > 0
IDENTITY> lf
EQ> lf = lf_test
IF> shock_lf_model > 0

@@

IDENTITY> part
EQ> part = part*1
IF> shock_part_model <= 0
IDENTITY> part
EQ> part = lf*1000/pop
IF> shock_part_model > 0
IDENTITY> part
EQ> part = lf*1000/pop
IF> shock_lf_model > 0

>>>>

COMMENT> 
BEHAVIORAL> lf
TSRANGE 2005 3 2020 1
EQ> lf = theta_00 + theta_01 * TSLAG(ur_ds,1)
COEFF> theta_00 theta_01
STORE> coe(102)

@@

@@

COMMENT>
IDENTITY> part
EQ> part = lf*1000/pop
